---
title: "Join Lab"
author: "Shikyna William"
date: "DATA 2401"
output: html_document
---


# Joins and `dplyr` practice

Load the `"nycflights13"` package.  You'll also need to load `dplyr` or `tidyverse`, if you didn't above.

```{r}
library(tidyverse)
#install.packages("nycflights13")
library(nycflights13)
my_flights <- flights # store my own version
my_flights <- na.omit(my_flights) ## this dataset has data on cancelled flights too, 
                                  ## so we 'll remove those for now
my_flights
```


Create a dataframe of the average arrival delays for each _destination_

```{r}
avg_arrival_delay <- my_flights %>%
  group_by(dest) %>% 
  summarise(avg_arriv_delay = mean(arr_delay))
avg_arrival_delay
```

Then use `left_join()` to join on the "airports" dataframe, which has the airport information.

```{r}
avg_arrival_delay <- left_join(avg_arrival_delay, airports, join_by(dest == faa))
airports
```


Note here: the column names don't match anymore! 

Which airport had the largest average arrival delay?

```{r}
avg_arrival_delay %>% slice_max(avg_arriv_delay, n=10) %>% select(dest, avg_arriv_delay)
avg_arrival_delay

#Or
avg_arrival_delay %>% arrange(-avg_arriv_delay) %>% slice_max(avg_arriv_delay) %>% select(dest, avg_arriv_delay)
```



What is the average departure delay for each airline? To answer this with something more than just the FAA code of the airline name, you need to create a dataframe of the average departure delay for each _airline_, then use `left_join()` to join on the "airlines" dataframe.


```{r}
my_flights
airlines
avg_dep_del <- my_flights %>%
  group_by(carrier) %>% 
  summarise(avg_dep_del = mean(dep_delay)) %>% 
  left_join(airlines)
avg_dep_del
```

Which airline had the smallest average departure delay? 



```{r}
avg_dep_del %>% slice_min(avg_dep_del)
```





Examples from R4DS:    

```{r}

top_dest <- flights %>%
  count(dest, sort = TRUE) %>%
  head(10)
top_dest

```

Now you want to find each flight that went to one of those destinations. You could, of course, filter. But! Now you can semi-join: 

```{r}
flights %>% 
  semi_join(top_dest)
```


What does anti_join(flights, airports, by = c("dest" = "faa")) tell you? What does anti_join(airports, flights, by = c("faa" = "dest")) tell you?
Perform the two joins below and consider what the results are. 
